Normalization: A pipeline to analyse time-course gene expression data

### 2019-02-16 scripts/02_differential_expression_analysis.Rmd
FIX taking the means of lfc for epicon-style computation

```{r de_analysis}
# Define contrast
de_analysis = data.frame(row.names=row.names(data))
for(contrast_formula in timecourse_contrasts){
    contrast = limma::makeContrasts(
	contrast_formula,
	levels=levels(meta$Group))
    model = moanin:::edgeWithContrasts(as.matrix(data), meta, contrast)
    contrast_name = gsub(" ", "", contrast_formula, fixed=TRUE)
    contrast_name_pval = paste(contrast_name, "-pval", sep="")
    contrast_name_qval = paste(contrast_name, "-qval", sep="")
    de_analysis[contrast_name_pval] = model$pval_lrt
    de_analysis[contrast_name_qval] = model$qval_lrt
}

>>>>

```{r de_analysis}
# Define contrast
de_analysis = data.frame(row.names=row.names(data))
for(contrast_formula in timecourse_contrasts){
    contrast = limma::makeContrasts(
	contrast_formula,
	levels=levels(meta$Group))
    model = moanin:::edgeWithContrasts(as.matrix(data), meta, contrast)
    contrast_name = gsub(" ", "", contrast_formula, fixed=TRUE)
    contrast_name_pval = paste(contrast_name, "-pval", sep="")
    contrast_name_qval = paste(contrast_name, "-qval", sep="")
    de_analysis[contrast_name_pval] = model$pval_lrt
    de_analysis[contrast_name_qval] = model$qval_lrt

    # Now compute log fold change using different methods
    # XXX This fails very badly if the contrasts provided is wrong.
    log_fold_change_epicon = moanin::estimate_log_fold_change(
	data, meta, c(contrast_formula), method="epicon")
    contrast_name_lfc_epicon = paste(contrast_name, "-lfc_epicon", sep="")
    de_analysis[contrast_name_lfc_epicon] = log_fold_change_epicon

    # XXX Something is wrong with method max
    log_fold_change_max = moanin::estimate_log_fold_change(
	data, meta, c(contrast_formula), method="max")
    contrast_name_lfc_max = paste(contrast_name, "-lfc_max", sep="")
    de_analysis[contrast_name_lfc_max] = log_fold_change_max

}
